\documentclass[a4paper,11pt]{article}
\RequirePackage[T1]{fontenc}

\usepackage{times}
\usepackage{calc}
\usepackage[shortcuts]{extdash}

\usepackage{graphicx} 

\reversemarginpar

\usepackage[paper=letterpaper,
            marginparwidth=1.1in,     % Length of section titles
            marginparsep=.075in,       % Space between titles and text
            margin=0.5in,               % 1 inch margins
            tmargin=0.65in,
            includemp]{geometry}

\setlength{\parindent}{0in}

\usepackage[shortlabels]{enumitem}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{0em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newlist{bibsection}{itemize}{3}
\setlist[bibsection]{label=,leftmargin=\bibhang,%
        itemindent=-\bibhang,
        itemsep=\bibsep,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\newlist{bibenum}{enumerate}{3}
\setlist[bibenum]{label=[\arabic*],resume,leftmargin={\bibhang+\widthof{[999]}},%
        itemindent=-\bibhang,
        itemsep=0.05in,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\let\oldendbibenum\endbibenum
\def\endbibenum{\oldendbibenum\vspace{-.6\baselineskip}}
\let\oldendbibsection\endbibsection
\def\endbibsection{\oldendbibsection\vspace{-.6\baselineskip}}
\makeatother

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

\renewcommand{\section}[1]{\pagebreak[3]%
    \vspace{1.3\baselineskip}%
    \phantomsection\addcontentsline{toc}{section}{#1}%
    \noindent\llap{\scshape\smash{\parbox[t]{\marginparwidth}{\hyphenpenalty=10000\raggedright #1}}}%
    \vspace{-\baselineskip}\par}

\newcommand*\fixendlist[1]{%
    \expandafter\let\csname preFixEndListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\csname preFixEndListend#1\endcsname\vspace{-0.6\baselineskip}}}

\let\originalItem\item
\newcommand*\fixouterlist[1]{%
    \expandafter\let\csname preFixOuterList#1\expandafter\endcsname\csname #1\endcsname
    \expandafter\def\csname #1\endcsname{\let\oldItem\item\def\item{\pagebreak[2]\oldItem}\csname preFixOuterList#1\endcsname}
    \expandafter\let\csname preFixOuterListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\let\item\oldItem\csname preFixOuterListend#1\endcsname}}
\newcommand*\fixinnerlist[1]{%
    \expandafter\let\csname preFixInnerList#1\expandafter\endcsname\csname #1\endcsname
    \expandafter\def\csname #1\endcsname{\let\oldItem\item\let\item\originalItem\csname preFixInnerList#1\endcsname}
    \expandafter\let\csname preFixInnerListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\csname preFixInnerListend#1\endcsname\let\item\oldItem}}

\newlist{outerlist}{itemize}{3}
    \setlist[outerlist]{label=\enskip\textbullet,leftmargin=*}
    \fixendlist{outerlist}
    \fixouterlist{outerlist}

\newlist{lonelist}{itemize}{3}
    \setlist[lonelist]{label=\enskip\textbullet,leftmargin=*,partopsep=0pt,topsep=0pt}
    \fixendlist{lonelist}
    \fixouterlist{lonelist}

\newlist{innerlist}{itemize}{3}
    \setlist[innerlist]{label=\enskip\textbullet,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt}
    \fixinnerlist{innerlist}

\newlist{loneinnerlist}{itemize}{3}
    \setlist[loneinnerlist]{label=\enskip\textbullet,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt}
    \fixendlist{loneinnerlist}
    \fixinnerlist{loneinnerlist}

\newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\halfblankline}{\quad\vspace{-0.5\baselineskip}\pagebreak[3]}

\usepackage{doi}
\usepackage{url}

\urlstyle{same}
\providecommand*\emaillink[1]{\nolinkurl{#1}}
\providecommand*\email[1]{\href{mailto:#1}{\emaillink{#1}}}

\begin{document}

 {\hspace*{-\marginparsep minus \marginparwidth}%
\begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
\centering
{\LARGE \bfseries {Harshit Sharma}}\\
\vspace{0.1cm}
\href{mailto:hsharm62@asu.edu}{\texttt{hsharm62@asu.edu}} \\
\texttt{Contact:315-832-0553}\\
\textit{\href{https://scholar.google.com/citations?user=Ja7tYhcAAAAJ&hl=en}{Google Scholar}}, \href{https://www.linkedin.com/in/harshit-sharma27/}{LinkedIn},
\href{https://github.com/anotherphdgrad}{Github}
\rule{\columnwidth}{1.2pt}
\end{minipage}}
 
 \vspace{0.2cm}

\section{Education}
\vspace{0.1cm}
\textbf{Ph.D. Computer and Information Science},
\href{https://scai.engineering.asu.edu/}{Arizona State University, Tempe, AZ}
\hfill {(exp.) 05/27}
\\(GPA: \textbf{3.98/4.0})

\vspace{0.01cm}

\textbf{B.S. Computer and Information Science}, 
\href{https://www.bmsce.ac.in/}{BMS College of Engineering, Bangalore, India}
\hfill {2019}
\\ (GPA: \textbf{4.0/4.0})

\vspace{0.1cm}
\section{Experience}

\textbf{Graduate Research Associate, (Fulton Fellowship)},
\href{https://scai.engineering.asu.edu/}{
School of Computing and Augmented Intelligence, Arizona State University}\\
Supervised by \href{https://asalekin.github.io/}{Dr. Asif Salekin}
\hfill {2024--Present}
\begin{innerlist}
    \item Implemented AI-driven models for analyzing human-centric data in the \textit{Ubiquitous and Intelligent Sensing \href{https://uislab.github.io/}{(UIS) Lab}}, focusing on fairness, privacy, and interpretability.
    \item Pioneered diffusion-based generative models for acoustic-articulatory representation learning.
    \item Conceptualized novel fairness enhancing mechanisms for human-centric Federated learning using loss landscape properties.
    \item Building privacy and utility preserving synthetic data generation pipelines for human-centric data. 
    \item Worked with advanced UWB sensors (Estimote,Vayyar,Walabot) and point cloud data for detecting health biomarkers and human presence.
    \item Engineered deep learning solutions for real-time analysis of physiological signals (heart rate, skin conductance), IMU sensor data, and audio features (formants, MFCCs).
    \item Conducted fairness and explainability (XAI) evaluations using SHAP and LIME to interpret deep learning and machine learning models.
    \item Designed affect detection models leveraging thermal and RGB images for human emotion and stress recognition.
    \item Developed novel multi-modal fusion techniques integrating wearable sensor data (Empatica E4, Biopac) for psycho-physiological arousal analysis.
\end{innerlist}

\textbf{Research Assistant},
\href{https://ecs.syracuse.edu/}{Syracuse University, College of Engineering and Computer Science}\\
Supervised by \href{https://asalekin.github.io/}{Dr. Asif Salekin}
\hfill {2020--2024}

\vspace{0.1cm}

\textbf{Research Assistant},
\href{http://www.mind-labs.org/}{M.I.N.D Lab Syracuse University} 
\hfill {2019}\\
Supervised by \href{http://www.mind-labs.org/people/2017/2/24/mark-r-costa-1}{Dr. Mark Costa}
\begin{innerlist}
\item  Developed a NodeJS and Neo4j graph database backend for analyzing and collecting physiological data, supporting mindfulness interventions in AR/VR. 
\end{innerlist}

\section{Research Focus}
\vspace{0.1cm}

My research advances trust in multimodal human sensing by developing machine learning methods that are interpretable, fair, and privacy-preserving. I focus on algorithmic techniques that generalize across heterogeneous data sources, mitigate spurious correlations, and protect sensitive information in complex real-world environments. While my methods are evaluated in applications such as monitoring opioid use disorder (OUD), stuttering, depression, and stress, the core contribution lies in building trustworthy foundations for human-centered AI. My research integrates principles from machine learning, ubiquitous computing, and algorithmic fairness to support reliable and equitable sensing systems.
 
\section{Programming Competences}

\vspace{0.1cm}

\textbf{Languages and Libraries}:
Python, Julia, Java, C++, NodeJS, Android, Pytorch, Pytorch Mobile, Keras, Librosa, Optuna, Pandas, Numpy, Matplotlib, scikit-learn, SQL, SHAP, LIME, Captum, Praat, PraatIO, AI Fairness 360, Flower Framework  

\section{Mentoring}
\vspace{0.1cm}
\textbf{Teaching Assistant}
\hfill{2021-2022}
\begin{innerlist}
\item CIS 675 (Design and Analysis of Algorithms)
\item CIS 477 (Intro/Analysis of Algorithms)
\end{innerlist}
\vspace{0.5cm}

\section{Publications}

\begin{bibenum}

\item \textbf{Harshit Sharma}, Yi Xiao, and Asif Salekin. "From Wearables to Depth: Training-Time IMU Supervision for Contactless Stress Detection" (Under Submission IMWUT 2026)

\item \textbf{Harshit Sharma*}, Shaily Roy*\footnote{* Indicates equal contribution.}, and Asif Salekin. "CurvFed: Curvature-Aligned Federated Learning." \url{https://arxiv.org/abs/2404.19725} (Accepted IMWUT 2026).

\item \textbf{Harshit Sharma}, Hao Zhang, Jakub Krzych, Lawrence Jones, Asif Salekin and Sucheta Soundarajan. "From Lab to Farm: Characterizing UWB-Based TDOA Localization Reliability for Dairy Cattle Monitoring" (Poster). (Accepted for IEEE DCOSS-IoT 2026)   

\item Roy, Shaily, \textbf{Harshit Sharma}, Dan Adler, Tanzeem Choudhary and Asif Salekin. "Ethical Fairness without Demographics". (Under review IMWUT 2026).

\item Xiao, Yi, \textbf{Harshit Sharma}, Dessa Bergen-Cico, Asif Salekin. "ReSPIRE: Resilience-Conditioned Stress-Pretrained Inference for Craving Detection in Opioid Use Disorder". (Under review IMWUT 2026)

\item Villa-Sánchez, Bernardo, Alexandra M. Reed, \textbf{Harshit Sharma}, Asif Salekin, Brianna Branson, Elyana Chacon, and Sydney Y. Schaefer. "Examining task-related stress and engagement associated with a performance-based test of functional cognition in older adults" The American journal of occupational therapy 2026 (Under review)

\item Oesterle, Tyler S., Yi Xiao, Nicholas L. Bormann, Dessa K. Bergen-Cico, Benjamin Lai, \textbf{Harshit Sharma}, and Asif Salekin. 'Wearable-derived measures of stress physiology in patients with opioid use disorder treated with methadone: A stress-task study in a real-world clinic with healthy controls." Addiction 2025 (Under Major revisions)

\item Xiao, Yi, \textbf{Harshit Sharma}, Sawinder Kaur, Dessa Bergen-Cico, and Asif Salekin. "Human Heterogeneity Invariant Stress Sensing." Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies 9, no. 3 (2025): 1-42. \url{https://dl.acm.org/doi/abs/10.1145/3749465}

\item Xiao, Yi, \textbf{Harshit Sharma}, Victoria Tumanova, and Asif Salekin. "Psychophysiology-aided Perceptually Fluent Speech Analysis of Children Who Stutter." In Proceedings of the \emph{ACM/IEEE 16th International Conference on Cyber-Physical Systems} (with CPS-IoT Week 2025), pp. 1-11. 2025. \url{https://dl.acm.org/doi/abs/10.1145/3716550.3722019}.

\item Kaur, Sawinder, Avery Gump, Yi Xiao, Jingyu Xin, \textbf{Harshit Sharma}, Nina R. Benway, Jonathan L. Preston, and Asif Salekin. "CRoP: Context-wise Robust Static Human-Sensing Personalization." \emph{Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies} 9, no. 2 (2025): 1-34. \url{https://dl.acm.org/doi/abs/10.1145/3729483}.

\item Xiao, Yi, \textbf{Harshit Sharma}, Zhongyang Zhang, Dessa Bergen-Cico, Tauhidur Rahman, and Asif Salekin. "Reading Between the Heat: Co-Teaching Body Thermal Signatures for Non-intrusive Stress Detection." \emph{Proc. ACM Interact. Mob. Wearable Ubiquitous Technol.} 7, 4, Article 189 (December 2023), 30 pages. \url{https://doi.org/10.1145/3631441}.

\item Testa, Brian, Yi Xiao, \textbf{Harshit Sharma}, Avery Gump, and Asif Salekin. "Privacy Against Real-Time Speech Emotion Detection via Acoustic Adversarial Evasion of Machine Learning." \emph{Proc. ACM Interact. Mob. Wearable Ubiquitous Technol.} 7, 3, Article 126 (September 2023), 30 pages. \url{https://doi.org/10.1145/3610887}.

\item \textbf{Harshit Sharma}, Yi Xiao, Victoria Tumanova, and Asif Salekin. "Psychophysiological Arousal in Young Children Who Stutter: An Interpretable AI Approach." \emph{Proc. ACM Interact. Mob. Wearable Ubiquitous Technol.} 6, 3, Article 137 (September 2022), 32 pages. \url{https://doi.org/10.1145/3550326}.

\item Benway, Nina R., Jonathan L. Preston, Asif Salekin, Yi Xiao, \textbf{Harshit Sharma}, and Tara McAllister. "Classifying Rhoticity of /r/ in Speech Sound Disorder Using Age- and Sex-Normalized Formants." arXiv preprint \url{https://arxiv.org/abs/2305.16111} (2023). (Accepted INTERSPEECH 2023).

\item Benway, Nina R., Jonathan Preston, Elaine Hitchcock, Asif Salekin, \textbf{Harshit Sharma}, and Tara McAllister. "PERCEPT-R: An Open-access American English Child/Clinical Speech Corpus Specialized for the Audio Classification of /r/ Sound." OSF Preprints. May 27. \url{https://doi.org/10.31219/osf.io/8zdsg}. (Accepted INTERSPEECH 2022).

\item Agrawal, Arun Prakash, Ankur Choudhary, and \textbf{Harshit Sharma}. "An Empirical Study on the Issues of Traditional Defect Life Cycle in Agile Model." In \emph{International Conference on Advances in Engineering Science Management \& Technology (ICAESMT)-2019}, Uttaranchal University, Dehradun, India, 2019. Available at SSRN: \url{https://ssrn.com/abstract=3402842}.


\end{bibenum}

\section{Volunteering}

\begin{itemize}\setlength{\itemsep}{-0.25em}
    \item \textbf{Academic Program Senator}, \href{https://gradorg.syr.edu/}{Graduate Student Organization, Syracuse University} \hfill{2022-2023}
    \item \textbf{Reviewer ETRA 2021}, Workshop \hfill{2022}
    \item \textbf{Reviewer ISWC 2021}, Posters and Demo Session \hfill{2022}
    \item \textbf{Student Volunteer}, \href{https://ubicomp.org/ubicomp2022/}{UBICOMP 2022} \hfill{2022}
    \item \textbf{Reviewer CHI 2024}, \href{https://chi2024.acm.org/for-authors/case-studies/}{Case Studies} \hfill{2023}
    \item \textbf{Reviewer} \href{https://aisnet.org/page/ECISPage}{ECIS} \hfill{2023,2025}
    \item \textbf{Program Committee Artifact Evaluation}, \href{https://sensys.acm.org/2025/}{Sensys 2025} \hfill{2024}
    \item \textbf{Reviwer} \href{https://www.ubicomp.org/ubicomp-iswc-2025/}{IMWUT} \hfill{2024,2025,2026}
    \item \textbf{Reviewer} \href{https://www.ozchi.org/2025/}{OzCHI 2025} \hfill{2025}
    \item \textbf{Reviewer} \href{https://chi2026.acm.org/}{CHI 2026} \hfill{2025}
    \item \textbf{Reviewer} \href{https://humanrobotinteraction.org/2026/}{HRI 2026} \hfill{2025} 
\end{itemize}

\section{Fellowships / Grants}
\begin{itemize}\setlength{\itemsep}{-0.1em}
    \item Fulton Fellowship Award: $\$71,500$  \hfill {2024-2025}
    \item Lambda Research Grant Program  $\$500$ (cloud credits) \hfill{2026-2027} 

\end{itemize}

\section{Awards}
\begin{itemize}\setlength{\itemsep}{-0.1em}
    \item \href{https://recognition.asu.edu/Award/42c50349-d81d-4d42-9237-303abce922c2}{SUN Award, ASU} \hfill{2025}
    \item \href{https://www.youtube.com/watch?v=W1WmRsRgTjo}{Siemens, MakeIT Real Hackathon:} 1st Runner-up \hfill{2017}
\end{itemize}

\section{News Coverage}

\begin{itemize}\setlength{\itemsep}{-0.1em}
    \item Our on-going work on combining Artificial Intelligence with mindfulness-based practices to provide intervention for people with opioid use disorder was highlighted by Syracuse University: \href{https://www.syracuse.edu/stories/falk-addiction-studies-opioid-treatment/}{Link}
    \item Our work on Privacy against Real-Time Speech Emotion Detection via Acoustic Adversarial Evasion of Machine Learning was highlighted by Syracuse University: \href{https://ecs.syracuse.edu/about/news/smart-speakers-smarter-protection}{Link}
\end{itemize}




\end{document}

